\documentclass[11pt,a4paper,sans]{moderncv}
\nopagenumbers{}
\moderncvicons{marvosym} 
\usepackage[scale=0.8, margin=0.5in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{fontawesome}
\usepackage{comment}
\usepackage[dvipsnames]{xcolor}
\moderncvtheme[blue]{classic}
\moderncvstyle{classic}
%\moderncvstyle{oldstyle}
%\moderncvstyle{banking}
\usepackage[unicode]{hyperref}
\moderncvcolor{red}
\usepackage{CJKutf8}
\setlength{\hintscolumnwidth}{2.5cm}

\firstname{\texttt{\textcolor{red}{Cl\'{e}mence}}}
\familyname{\texttt{\textcolor{red}{R\'{e}da}}}
\title{PhD student in Genetics}
\email{clemence.reda@inria.fr}
\homepage{clreda.github.io}
\address{PROTECT UMR 1141, Point Jaune, Bât. Bingen\\48, boulevard Sérurier, 75019 Paris, France\\ \\}{}{}
\extrainfo{\faGithub{ \href{https://www.github.com/clreda}{clreda}}}

\begin{document}
\makecvtitle

\vspace{-1.5cm}
\section{Education}
\cventry{2019 -- present}{Doctorat}{Université de Paris, Inserm UMR 1141 \& CNRS UMR 9189}{}{}{PhD in Genetics : \textbf{Combination of gene regulatory
networks and sequential machine learning for drug repurposing}, supervised by  \textcolor{blue}{\href{http://neurodiderot.org/index.php/en/delahaye-en/}{Pr. Andr\'{e}e Delahaye-Duriez}} \& \textcolor{blue}{\href{http://chercheurs.lille.inria.fr/ekaufman/}{Dr. \'{E}milie Kaufmann}}.\\}
\cventry{2018 -- 2019}{M2 Master Vision, Apprentissage (MVA)}{\'{E}cole Normale Supérieure$^*$ (ENS) Paris-Saclay}{(ex-\'{E}cole Normale Supérieure de Cachan)}{}{Master's degree in Machine Learning. (\emph{summa cum laude}, equiv.  GPA: $4.0$, no ranking)\\}
\cventry{2017 -- 2018}{Année de Recherche Pr\'{e}doctorale \`{a} l'\'{E}tranger (ARPE)}{ENS Paris-Saclay}{}{}{Ten-month long research internship at the Faculty of Mathematics, Informatics and Mechanics (MIM UW) of the University of Warsaw (Poland) included in the curriculum of ENS Paris-Saclay. Proof-of-concept on the explicit inclusion of biological interactions in gene regulatory networks and its impact on inference and simulation of transcriptomic regulation, in research team \textbf{Regulomics} supervised by \textcolor{blue}{\href{http://bioputer.mimuw.edu.pl/~bartek/}{Dr. Bartek Wilczy\'{n}ksi}}.\\  (Final grade (equiv. GPA): $4.0$, no ranking)\\}
\cventry{2016 -- 2017}{M1 Master Parisien en Recherche en Informatique (MPRI)}{ENS Paris-Saclay}{}{}{Master's degree in Computer Sciences. (\emph{summa cum laude}, equiv.  GPA: $4.0$, rank: $3/25$)\\}
\cventry{2015 -- 2016}{L3 Licence informatique fondamentale ENS Cachan}{\'{E}cole Normale Supérieure de Cachan}{}{}{Bachelor's degree in Computer Sciences. (\emph{cum laude}, equiv.  GPA: $4.0$, rank: $10/26$)\\}

$^*$ \small{\'{E}cole Normale Supérieures are selective French schools for research and teaching.}

\begin{comment}
\subsection{Formations doctorales}
\cvitem{Sept. 2020\\ (3 jours)}{\textbf{FAIR 2020} : ``\textcolor{blue}{\href{https://ressources.france-bioinformatique.fr/fr/evenements/principes-fair-appliques-a-la-bioinformatique}Les principes FAIR appliqués à la bioinformatique}'' \hspace{5cm} (Institut Français de Bioinformatique, IFB)\\}
\cvitem{2019\\(3 mois)}{\textbf{Pr. Walter Fontana} : ``\textcolor{blue}{\href{https://www.college-de-france.fr/site/walter-fontana/course-2019-2020.htm}{La biologie de l'information – un dialogue entre l'informatique et la biologie}}'' (Coll\`{e}ge de France)}
\cvitem{Juil. 2019\\(2 semaines)}{\textbf{RLSS 2019} : ``\textcolor{blue}{\href{https://rlss.inria.fr/}{Reinforcement Learning Summer}}'' (Inria SCOOL)}
\end{comment}

\section{Previous Work Experiences}

\subsection{Research internships}
\cventry{2019\\(4 months)}{Teams \textbf{Integrative Genomics} (PROTECT UMR 1141) \& \textbf{SCOOL/CRIStAL} (UMR 9189)}{Supervision by \textcolor{blue}{\href{http://neurodiderot.org/index.php/en/delahaye-en/}{Pr. Andr\'{e}e Delahaye-Duriez}} and \textcolor{blue}{\href{http://chercheurs.lille.inria.fr/ekaufman/}{Dr. \'{E}milie Kaufmann}}}{Paris \& Villeneuve d'Ascq, France}{}{Design of a drug repurposing method through a bandit algorithm combined with the prediction of transcriptomic states by a gene regulatory network. Application to the prediction of new anti-epileptics.\\}
\cventry{2017\\(5 months)}{Team \textbf{Genomics and Regulatory Systems Unit, Okinawa Institute of Science and Technology (OIST)}}{Supervision by \textcolor{blue}{\href{https://www.crick.ac.uk/research/labs/nicholas-luscombe}{Dr. Nicholas Luscombe}} and \textcolor{blue}{\href{https://www.ebi.ac.uk/about/people/garth-ilsley}{Dr. Garth Ilsley}}}{Onna-son, Japon}{}{Design and implementation of a single-cell RNA sequencing clustering method taking into account intergene expression dependencies using a probabilistic model~; implementation in R Shiny of a web application for the visualisation and preliminary analysis of single-cell RNA sequencing data. Application to transcriptomic data analysis in ciona (\emph{Ciona intestinalis}).\\}
\cventry{2016\\(2 months)}{Centre de Bioinformatique de Bordeaux (CBiB)}{Supervision by  \textcolor{blue}{\href{https://www.labri.fr/perso/macha/}{Dr. Macha Nikolski}} and le \textcolor{blue}{\href{https://mabiovis.labri.fr/#team}{Dr. Mathieu Raffinot}}}{Bordeaux, France}{}{Design and implementation of compared analyses of taxonomic trees built from metagenomic data. Application to the analysis of data from intestinal guts of children afflicted with cystic fibrosis at H\^{o}pital Pellegrin in Bordeaux.\\}

\subsection{Teaching \& Mentoring Experiences}
\cventry{2020 -- 2021\\(64 hours a year)}{Doctorant Contractuel avec Mission d'Enseignement (DCME) (Teaching Assistant)}{Biostatistics, programming and bioinformatics}{Universit\'{e} de Paris, UFR Sciences de la Vie}{}{}
\cventry{2020\\ (6 months)}{Supervision of a Masters's degree internship}{Joint supervision of a Masters intern on the analysis of targeted single-cell RNA sequencing data of inflammatory microglia in development}{Inserm}{}{}
\cventry{2019 -- 2020\\(2 months)}{Supervision of a Masters's degree project}{Proposal of a project on drug repurposing based on collaborative filtering, and joint supervision of a Masters student in the course \textbf{Graphs in Machine Learning} in masters \textbf{MVA} (2020)}{ENS Paris-Saclay}{}{}

\section{Grants}
\cventry{2019}{Research program for project REPOS}{Inserm-CNRS ``\textcolor{blue}{\href{https://www.cnrs.fr/mi/IMG/pdf/sante_numerique_texte_aap.pdf}{Digital health challenge}}'' AAP 2019 (1 year)}{}{}{}
\cventry{2019 -- 2022}{PhD scholarship}{Contrat Doctoral Sp\'{e}cifique aux Normaliens (CDSN) 2019}{ENS.X19RDTME-SACLAY19-22 (3 years)}{}{}

\section{Research}
\subsection{Papers}
\cventry{2021}{Dealing With Misspecification In Fixed-Confidence Linear Top-m Identification}{\underline{C. Réda}, {A}. Tirinzoni \& R. Degenne}{[\textit{research, \textcolor{blue}{\href{https://neurips.cc/Conferences/2021/Schedule?type=Poster}{accepted}}}]}{Proceedings of the $35^{th}$ Conference on Neural Information Processing Systems (NeurIPS 2021), HAL: \textcolor{blue}{\href{https://hal.archives-ouvertes.fr/hal-03409205}{03409205}}. Impact factor : 33.5}{}{}
\cventry{}{Top-$m$ identification for linear bandits}{\underline{C. Réda}, \'{E}. Kaufmann \& A. Delahaye-Duriez}{[\textit{research}]}{Proceedings of the $24^{th}$ International Conference on Artificial Intelligence and Statistics 2021 (AISTATS 2021), 130, HAL: \textcolor{blue}{\href{https://hal.archives-ouvertes.fr/hal-03172145}{03172145}}. Impact factor : 9.9}{}{}
\cventry{2020}{Machine learning applications in drug development}{\underline{C. Réda}, \'{E}. Kaufmann \& A. Delahaye-Duriez}{[\textit{review}]}{Computational and Structural Biotechnology Journal, 18, 241-252, DOI : \textcolor{blue}{\href{https://doi.org/10.1016/j.csbj.2019.12.006}{10.1016/j.csbj.2019.12.006}}. Impact factor : 6.0}{}
\cventry{}{Automated inference of gene regulatory networks using explicit regulatory modules}{\underline{C. Réda} \& B. Wilczy\'{n}ski}{[\textit{research}]}{Journal of Theoretical Biology, 486, DOI : \textcolor{blue}{\href{https://doi.org/10.1016/j.jtbi.2019.110091}{10.1016/j.jtbi.2019.110091}}. Impact factor : 2.3}{}
\cventry{2019}{Identification de cibles thérapeutiques et repositionnement de médicaments par analyses de réseaux géniques}{A. Delahaye-Duriez, \underline{C. Réda} \& P. Gressens}{[\textit{review}]}{M\'{e}decine/Sciences, 35(6-7), 515-518, DOI : \textcolor{blue}{\href{https://doi.org/10.1051/medsci/2019108}{10.1051/medsci/2019108}}. Impact factor : 0.7}{}

\subsection{Talks}
\cventry{February 2022}{DSABNS 2022}{\underline{C. Réda}.
\textnormal{Gene network oriented drug discovery: automated inference of Boolean networks for drug target prediction (talk)}}{}{}{}
\cventry{December 2021}{NeurIPS 2021}{\underline{C. Réda}.
\textnormal{Dealing With Misspecification In Fixed-Confidence Linear Top-m Identification (poster)}}{}{}{}
\cventry{April 2021}{AISTATS 2021}{\underline{C. Réda}.
\textnormal{Top-$m$ identification for linear bandits (poster)}}{}{}{}
\cventry{October 2020}{Journ\'{e}es de recherche respiratoire (J2R) 2020}{\underline{C. Réda}. \textnormal{Transcriptome of neurons in a model of Congenital Central Hypoventilation Syndrome (poster)}. Conference has been cancelled due to the pandemic}{}{}{}
\cventry{July 2020}{Journées Ouvertes de Biologie, Informatique et Mathématique (JOBIM) 2020}{\underline{C. Réda}. \textnormal{Automated inference of gene regulatory networks using explicit regulatory modules (oral)}}{}{}{}
\cventry{Sept. 2018}{Workshop 6, European Conference on Computational Biology (ECCB) 2018}{\underline{C. Réda}. \textnormal{Automated inference of gene regulatory networks using explicit regulatory modules (oral)}}{}{}{}
\cventry{June 2018}{BioInformatics in Toru\'{n} (BIT) 2018}{\underline{C. Réda}. \textnormal{Automated inference of gene regulatory networks using explicit regulatory modules (oral)}}{}{}{}

\section{Commitment to popularization of sciences and law making}
\subsection{Popularization of sciences}
\cvitem{December 2016 -- Sept. 2018}{\textbf{Published on} \textcolor{blue}{\href{https://tryalgo.org/fr/}{Tryalgo}} [in French] : series of blog posts on known algorithms with concrete applications, aimed at high school and college students (approx. $2,400$ unique monthly users~; two of these posts constitute the Top-$2$ most visited pages.} 
\cvitem{October2016}{\textbf{Published on} \textcolor{blue}{\href{https://www.lemonde.fr/blog/binaire/2016/10/17/a-p-b-la-vie-apres-le-bac/}{Binaire}} (blog on Computer Science affiliated with the newspaper Le Monde) \textbf{and} \textcolor{blue}{\href{https://theconversation.com/apb-la-vie-apres-le-bac-66848}{The Conversation}} [in French] : ``A.P.B. : La vie après le bac'' (conjointy written with \textcolor{blue}{\href{https://www.inria.fr/en/serge-abiteboul}{Serge Abiteboul}}). Explanation of the algorithm of Gale-Shapley which has been in use in a previous version of the French national web application for high school students' applications to college} 
\subsection{Popularization of law-making}
\cvitem{December 2016 -- Sept. 2018}{\textbf{Published on} \textcolor{blue}{\href{https://reflechir.fr/}{R\'{e}fl\'{e}chir.fr}} [in French] : series of blog posts on laws passed since 2017 in France: explanation of their content and their consequences ($534$ followers on February, $24$ $2021$).} 

\section{Language proficiency}
\cvitemwithcomment{French}{C2}{Native speaker.}
\cvitemwithcomment{English}{C1}{TOEFL score (in 2016): 643/677.}
\cvitemwithcomment{Spanish}{B1}{Intermediate level, studied at school for seven years.}

\end{document}